### 2017-01-09 paper/evaluation.tex
updates

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost from a regression-test is distributed
among the test cases?}
\newcommand{\RQC}{How often parallelization features appear in
build files?}
\newcommand{\RQD}{What is the impact of parallelization?}
\newcommand{\RQE}{What factors contribute to improve performance
through parallelization?\Jbc{Previously as "When does parallelization
works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of parallelization?}

@@

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    deletekeywords={true}
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=
    stars:>=100+language:java+mvn%20in:readme+
    pushed:>=2016-01-01+sort:stars

\end{lstlisting}
    \caption{\label{fig:subject-query} Query to the \github{} API for
    projects with the following criteria: (1) Java, (2) at least 100
    stars, (3) updated on January 1st, 2016 (or later), (4) contains
    the string \emph{mvn} in the \emph{readme} file. Output is
    paginated in descending order of stars.}
\end{figure}

A Maven project may contain several submodules with multiple
\emph{pom.xml} files. We considered only projects with a
\emph{pom.xml} file located in the root directory.  As of December
30th 2016, our search criteria returned 615 subjects. From the
\numSubjsTotal{} downloaded projects, 46 were not Maven projects and
159 were in a unstable revision. From these 159 unstable subjects,
\Jbc{elaborate what is unstable (eg, (1) how many could not resolve
dependencies? (2) how many could not compile sources and tests? (3)
could not run tests due to incompatible testing environment?}. Our
final set consists in \numSubjs{} testable subjects.

@@

Given that \percentMedLongRunning{} of the projects are costly (\ie,
\numMedLong{} projects from \medg{} and \longg{}), we concluded that
time-consuming regression test suites are relatively frequent in
open-source projects.  It is important to mention that
Figure~\ref{fig:rq1-barplot} represents a lower bound for time cost:
some tests may finish early due to a failure since a subject may be
tested in a potentially unstable revision. From the \numSubjs{}
projects, 286 passed all tests and 118 had failures. \Jbc{elaborate
failed subjects: how much \% of the tests failed?}

@@

To evaluate the presence of parallelization settings, we considered
the \numMedLong{} subjects from the \longg{} and \medg{} groups
identified in Section~\ref{sec:rqA}. We focused on these two groups
because given that costly test suites exist, we wanted to analyze if
their maintainers are aware of parallelization settings and how they
use these settings.  We computed the frequency of the parallelism
modes (see Section \ref{sec:modes}) using a semi-automatic approach:
we first discover automatically the relevant build files (\ie,
\emph{pom.xml} files) and then we manually inspect the files to
eliminate false-positives (\eg, a false-positive may occur if the file
contains a commented configuration).  Figure~\ref{fig:discovery-step}
describes the discovery step: first, we list the paths of all build
file and then we filter only the build files that contain any of the
keywords, \CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}.
Notice that, for Maven projects, any of these keywords exist in any
possible parallelism configuration \Fix{cite surefire doc}.

@@

From the \numMedLong{} subjects, the discovery step checked \Fix{X}
files and yielded \Fix{Y} files to inspect (distributed in \Fix{A}
subjects). \Jbc{How many were valid configurations? Show a contingency
table summarizing results for Medium/Long when we have the results}
\Jbc{Show a histogram with the distribution of parallel modes}.

>>>>

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost from a regression-test is distributed
among the test cases?}
\newcommand{\RQC}{How often parallelization settings appear in
build files?}
\newcommand{\RQD}{What is the impact of parallelization?}
\newcommand{\RQE}{What factors contribute to improve performance
through parallelization?\Jbc{Previously as "When does parallelization
works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of parallelization?}

@@

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    deletekeywords={true}
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=language:java
        +stars:>=100+pushed:>=2016-01-01
        +mvn%20in:readme+sort:stars
\end{lstlisting}
    \caption{\label{fig:subject-query} Query to the \github{} API for
    projects with the following criteria: (1) Java, (2) at least 100
    stars, (3) updated on January 1st, 2016 (or later), (4) contains
    the string \emph{mvn} in the \emph{readme} file. Output is
    paginated in descending order of stars.}
\end{figure}

A Maven project may contain several sub-modules with multiple \pomf{}
files. We considered only projects with a \pomf{} file located in the
root directory.  As of December 30th 2016, our search criteria
returned \numSubjsTotal{} subjects. From the \numSubjsTotal{}
downloaded projects, 46 were not Maven projects (or did not have a
\pomf{} in the root directory) and 159 were in a unstable revision.
From these 159 unstable subjects, \Jbc{elaborate what is unstable (eg,
(1) how many could not resolve dependencies? (2) how many could not
compile sources and tests? (3) could not run tests due to incompatible
testing environment?}. Our final set consists in \numSubjs{} testable
subjects.

@@

Given that \percentMedLongRunning{} of the projects are costly (\ie,
\numMedLong{} projects from \medg{} and \longg{}), we concluded that
time-consuming regression test suites are relatively frequent in
open-source projects.  It is important to mention that
Figure~\ref{fig:rq1-barplot} represents a lower bound for time cost:
some tests may finish early due to a failure since a subject may be
tested in a failing revision. From the \numSubjs{} projects, 286
passed all tests and 118 had failures. \Jbc{elaborate failed subjects:
how much \% of the tests failed?}

@@

\Jbc{I'm currently considering only the long group but as soon as I
have the remaining results, I will update the plots} To evaluate the
presence of parallelization settings, we considered the \numMedLong{}
subjects from the \longg{} and \medg{} groups identified in
Section~\ref{sec:rqA}. We focused on these two groups because given
that costly test suites exist, we wanted to investigate if their
maintainers are aware of parallelization settings and how they use
these settings (see Section \ref{sec:modes}).  We computed the
frequency of the parallelism modes using a two-steps approach: the
first step (discovery) automatically finds relevant build files
(\ie, \pomf{} files with parallelization settings); the second step
(inspection) consists in a manual inspection to confirm the presence
of parallelism settings in the build file and classify them according
to the parallelism level (see Section \ref{sec:modes}).
Figure~\ref{fig:discovery-step} describes the discovery step: we list
the paths of all build files and filter only the files that contain
any of the keywords \CodeIn{forkMode}, \CodeIn{forkCount}, or
\CodeIn{parallel}.  Notice that, for Maven projects, any of these
keywords exist in any possible parallel setting \Fix{cite surefire
doc}. Our first step is complete but is not sound since the line that
matches one of keywords may not represent part of a real setting (\eg,
comments).  We eliminate false-positives in the confirmation step.
From the \numMedLong{} subjects, the discovery step found 2853 files
and filtered 109 relevant files. Later, from the 109 relevant files,
we confirmed \Fix{M} valid settings from \Fix{X} subjects.
Table~\ref{tab:inspection-table} summarizes the results from the file
inspection and Figure~\ref{fig:freqmodes} shows the distribution of
parallelism modes from the \Fix{M} settings.

@@

\begin{table}[h!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccccc}
        \toprule%
        Group  & Build Files & Filtered files & Settings & Subjects \\%
        \midrule%
        Long   & 1613 & 79 & \Fix{X} & \Fix{X}\\%
        Medium & 1240 & 30 & \Fix{X} & \Fix{X}\\%
        \midrule%
        Total  & 2853 & 109 & \Fix{X} & \Fix{X}\\%
        \bottomrule%
    \end{tabular*}
    \caption{\Fix{to-be-defined}}
    \label{tab:inspection-table} 
\end{table}

\begin{figure}[h!]
    \centering
    \Fix{to appear}
    \caption{\label{fig:freqmodes}Distribution of parallelism modes
    identified in \Fix{M} }
\end{figure}
